%-------------------------
% Resume in Latex
% Author : Yi Hern
% Adopted from https://github.com/arasgungore/arasgungore-CV/blob/main/main.tex
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \text{\small#3} & \text{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \text{\small#1} & \text{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & #2 \\
    \end{tabular*}\vspace{-18pt}
}

\newcommand{\resumeEducationItem}[2] {
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{\small #1} & \text{\small #2} \\
    \end{tabular*}\vspace{-8pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-10pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Yi Hern, Lee} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:+65 97248903}{(+65) 9724 8903}
    $|$
    \faAt \hspace{.5pt} \href{mailto:leeyihern99@gmail.com}{leeyihern99@gmail.com}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/yi-hern-lee/}{LinkedIn}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/YiHern-Lee}{GitHub}
    % $|$
    % \faGlobe \hspace{.5pt} \href{link_here}{Portfolio}
\end{center}



%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart
    
    \resumeEducationHeading
      {National University of Singapore
      }{Singapore}
      \resumeEducationItem {Bachelor of Computing in Computer Science (Honours)}
      {Aug 2020 | Dec 2024}
      \resumeItemListStart
        \resumeItem{GPA: 4.58/5.0}
        \resumeItem{Focus area in Algorithms and Theory}
        \resumeItem{Study Abroad at University of North Carolina, Chapel Hill for Fall Semester 2022}
      \resumeItemListEnd
      \resumeEducationItem {Bachelor of Business Administration (Double Degree Program)}{}
      \resumeItemListStart
        \resumeItem{GPA: 4.56/5.0}
        \resumeItem{Focus area in Business Analytics}
      \resumeItemListEnd
      \vspace{-4pt}
\resumeSubHeadingListEnd


%----------- EXPERIENCE -----------

\section{Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {TikTok}{Singapore}
      {Software Engineer, Intern}{Jan 2024 | Aug 2024}
        \resumeItemListStart
            \resumeItem{Joined the Global E-Commerce Data Intelligence Backend Team, focusing on providing data insights and recommendations to B-side TikTok Shop external users.}
            \resumeItem{Designed and developed endpoints for a new backend service, Campaign Workbench, that serves sales campaign data for sellers. Features allowed sellers to be notified of their products' stock status and handle them in real-time. Launched on USA 6.6 Summer Sale, with over 1,200 merchants onboard.}
            \resumeItem{Led refactoring efforts for the codebase of Export Platform, an internal service that supports bulk export of data from RPC endpoints. Developed custom concurrency module with rate limiting to optimize data fetching and cut latency of exports by up to 50\%.}
            \resumeItem{Developer for Live Workbench, a service that focuses on serving livestreaming e-commerce data to sellers and content creators. Developed requested features, followed up on bug reports, and performed technical improvements.}
        \resumeItemListEnd

    \resumeSubheading
      {Diaim Consulting}{Singapore}
      {Software Engineer, Freelance}{Jun 2023 | Aug 2023}
        \resumeItemListStart
            \resumeItem{Diaim Consulting is a small-sized marketing consulting firm based in Singapore. Worked closely with the founders to advise on, and implement technical solutions for their needs.}
            \resumeItem{Developed Telegram bot for a marketing campaign for a new F&B outlet in NUS. Bot tracks user referrals on a Telegram group and encourages more participants to invite their friends. Managed to attract over 1000 students to join in the promotional group, resulting in high visibility and awareness at launch}
            \resumeItem{Created a business website for a local bakery, in collaboration with the in-house web designers. Built, hosted, and configured a custom domain for the website. Utilized React, HTML, and CSS.}
        \resumeItemListEnd

    \resumeSubheading
      {Shopee (Sea Limited)}{Singapore}
      {Software Engineer, Intern}{Feb 2022 | Aug 2022}
        \resumeItemListStart
            \resumeItem{Joined the Product Page Backend Team, which focuses on serving product descriptions, and facilitate users' checkout journey.}
            \resumeItem{Designed and executed development for a Backend service optimization project. Migrated endpoints to a new codebase that leverages increased concurrency for lower latency.}
            \resumeItem{Designed and implemented features for internal SLI monitoring. Project aims to increase ease of live service monitoring and detection of service degredation. Feature allows SLI metrics to be visualized alongside with featured dates, such as sales campaigns and scheduled code releases.}
            \resumeItem{Researched and developed technical project on the topic of TCP pooling to handle high amounts of concurrent requests between microservices. Code written in Golang.}
        \resumeItemListEnd
    
    \resumeSubheading
      {National University of Singapore, School of Computing}{Singapore}
      {Undergraduate Tutor, Part-Time}{Aug 2021 | May 2023}
        \resumeItemListStart
            \resumeItem{Tutor for undergraduate Computer Science classes.}
            \resumeItem{Conducted tutorial and lab classes for 25-40 undergraduate students for courses CS1010E - Programming Methodology (Python), and CS2040 - Data Structures and Algorithms (Java).}
            \resumeItem{Demonstrated strong proficiency in teaching programming concepts, and received positive feedbacks from students.}
        \resumeItemListEnd
    
    
  \resumeSubHeadingListEnd

%----------- SKILLS -----------

\section{Skills}
\vspace{2pt}
\resumeSubHeadingListStart
  \small{\item{
      \textbf{Languages:}{ Go, Java, C++, Python} \\ \vspace{3pt}
      \textbf{Technologies:}{ Git, Protobuf, Thrift, MySQL, Spark, Google Cloud Platforms } \\ \vspace{3pt}
  }}
\resumeSubHeadingListEnd

%----------- PROJECTS -----------

\section{Projects}
    \vspace{3pt}
    \resumeSubHeadingListStart
      
      \resumeProjectHeading
        {\textbf{Static Program Analyzer}}{Aug 2023 | Nov 2023}
          \resumeItemListStart
            \resumeItem{C++ Project to parse and extract relations between functions, variables, and line of code for programs written in SIMPLE language.}
            \resumeItem{Designed and developed the Query Evaluator engine to answer queries. Utilized partial result caching and various optimizations to achieve top percentile in performance.}
          \resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{Portfolio Risk Management}}{Aug 2023 | Nov 2023}
          \resumeItemListStart
            \resumeItem{Python Project to analyze various industry's historical returns to re-weigh a portfolio.}
            \resumeItem{Performed data cleaning, covariance shrinkage, and utilized various financial models, such as CAPM, HERC2, to forecast the best performing portfolio.}
          \resumeItemListEnd

    \resumeProjectHeading
        {\textbf{Applicant Tracking System}}{Jan 2022 | May 2022}
        \resumeItemListStart
            \resumeItem{Command-line based application written in Java for recruiter's to track applicant's information and status throughout recruitment process.}
            \resumeItem{Utilized a Model-View-Controller architecture.}
        \resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{StudentConnect}}{May 2021 | Aug 2021}
          \resumeItemListStart
            \resumeItem{Web-app to facilitate communication and exchange of academic resources.}
            \resumeItem{Developed with a front-end techstack of React and React-Redux, and a back-end techstack of NodeJS, Cloud Functions and Cloud Firestore.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%----------- Miscellaneous -----------

\section{Misc}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Leadership:}{ Served as a Third Sergeant in the Singapore Armed Forces. Led a section of Medics for an emergency response force.} \\ \vspace{3pt}

        \textbf{Language:}{ Natively bilingual in English and Mandarin Chinese.} \\ \vspace{3pt}
    
        \textbf{Work Authorization:}{ Singaporean Citizen} \\ \vspace{3pt}
    }}
  \resumeSubHeadingListEnd


%----------- RELEVANT COURSEWORK -----------

% \section{Relevant Coursework}
  % \vspace{2pt}
  % \resumeSubHeadingListStart
    % \small{\item{
        % \textbf{Major coursework:}{ Materials Science, Electrical Circuits I-II, Digital System Design, Numerical Methods, Probability Theory, Electronics I-II, Signals and Systems, Electromagnetic Field Theory, Energy Conversion, System Dynamics and Control, Communication Engineering, Pattern Recognition, Introduction to Digital Signal Processing, Introduction to Digital Communications, Introduction to Database Systems, Introduction to Image Processing, Machine Vision} \\ \vspace{3pt}
        
        % \textbf{Minor coursework:}{ Discrete Computational Structures, Introduction to Object-Oriented Programming, Data Structures and Algorithms, Computer Organization, Fundamentals of Software Engineering}
    % }}
  % \resumeSubHeadingListEnd



%----------- CERTIFICATES -----------

% \section{Certificates}
  % \resumeSubHeadingListStart
    
    % \resumeOrganizationHeading
      % {Procter \& Gamble VIA Certificate Program}{Feb 2022}{Project Management and Personal Productivity}
    
  % \resumeSubHeadingListEnd



%----------- ORGANIZATIONS -----------

% \section{Organizations}
  % \resumeSubHeadingListStart
    
    % \resumeOrganizationHeading
      % {Institute of Electrical and Electronics Engineers (IEEE)}{Feb 2022 -- Present}{Student Member}
    
  % \resumeSubHeadingListEnd



%----------- HOBBIES -----------

% \section{Hobbies}
  % \resumeSubHeadingListStart
    % \small{\item{Basketball, Swimming, Fitness, Eight-ball, Horology}}
  % \resumeSubHeadingListEnd



%----------- REFERENCES -----------

% \section{References}
  % \vspace{2pt}
  % \resumeSubHeadingListStart
    % \item{References available upon request.}
  % \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}